Research log

### 2024-08-22 docs/preregisteredMethodsAndResults.Rmd
paths

# save(E4.click_log, file='E4.click_log.RData')

load('E4.click_log.RData')
```

@@

# save(E4.click_log_with_boards, E4.click_log_with_boards_random,
# E4.click_log_with_boards_most_frequent, E4.click_log_with_boards_optimal,
# E4.letter_prob_click_log_with_boards,
# E4.letter_prob_click_log_with_boards_random,
# E4.letter_prob_click_log_with_boards_optimal,
# file='E4.click_log_with_boards.RData')

load('E4.click_log_with_boards.RData') # this file includes all the above dataframes.

@@

load('E4.judge_df.RData')

>>>>

# save(..experiments/Hangman2/data/E4.click_log, file='E4.click_log.RData')

load('..experiments/Hangman2/data/E4.click_log.RData')
```

@@

# save(E4.click_log_with_boards, E4.click_log_with_boards_random,
# E4.click_log_with_boards_most_frequent, E4.click_log_with_boards_optimal,
# E4.letter_prob_click_log_with_boards,
# E4.letter_prob_click_log_with_boards_random,
# E4.letter_prob_click_log_with_boards_optimal,
# file='../experiments/Hangman2/data/E4.click_log_with_boards.RData')

load('../experiments/Hangman2/data/E4.click_log_with_boards.RData') # this file includes all the above dataframes.

@@

load('../experiments/Hangman2/data/E4.judge_df.RData')
